A generalized definition of multidimensional item response theory parameters

### 2024-07-05 output/paper_draft/paper_M2PLM_parameters.Rmd
Corrects computation of oblique coordinates
Correctly states the computation of the oblique coordinates (as by a "parallellepiped" with the axes), instead of the "orthogonal projections" on the axes, as was incorrectly stated before.

The aforementioned properties are easier to apprehend with
a visual representation of the items.
A vector plot [@ackerman_creating_1994] is the most appropriate way of
representing the items graphically;
it allows one to plot several items altogether and analyze them
in terms of their multidimensional parameters [@ackerman_graphical_1996]:
An item vector will be applied at a direction and (signed) distance
from the origin of the coordinate system given by its $`r MIL_PARAM`$ parameter
and will have a length equal to its $`r MDISC_SYM`$ parameter.

As plotting more than two dimensions is difficult on a bidimensional display
(and hardly possible at all for more than three dimensions with the
currently available technology),
we will limit ourselves to the bidimensional case here.
Plotting on a two-dimensional display usually requires providing
coordinates in a rectangular Cartesian system.
Therefore, we will need to compute the equivalent rectangular coordinates
of our general, possibly non-rectangular coordinates.
However, this implies pre-multiplying by $`r TRANSFORM_MATRIX`$,
instead of $`r TRANSFORM_MATRIX_TRANSP_INV`$ as would be expected from
Equation \@ref(eq:discr-vector-std).
This is because computing the equivalent rectangular coordinates
of the oblique ones is different from computing the item parameters
transformed to an orthogonal space.
While the latter implies rotating the axes to an orthogonal configuration and
computing the new coordinates in these axes,
the former implies transforming the space altogether along with the
axes transformation.

Therefore, we need to define a convenient value for $`r TRANSFORM_MATRIX`$
that allows us to represent the test space structure
and the items by transforming their coordinates to
a rectangular Cartesian system.
However, to facilitate the interpretation,
we want to avoid changing the scaling of the parameters.
We will thus prefer the correlation-based over the covariance-based parameters.
Thus, we define $`r TRANSFORM_MATRIX`$ such that
$`r TRANSFORM_MATRIX_TRANSP_INV`$ is a square root matrix of $`r CORR_MATRIX`$.

@@

1. Define $`r TRANSFORM_MATRIX`$ such that $`r TRANSF_MATRIX_SQ_CORR_INV_EQ`$.

@@

>>>>

The aforementioned properties are easier to apprehend with
a visual representation of the items.
A vector plot [@ackerman_creating_1994] is the most appropriate way of
representing the items graphically;
it allows one to plot several items altogether and analyze them
in terms of their multidimensional parameters [@ackerman_graphical_1996]:
An item vector will be applied at a direction and (signed) distance
from the origin of the coordinate system given by its $`r MIL_PARAM`$ parameter
and will have a length equal to its $`r MDISC_SYM`$ parameter.
Its direction will also be given by the direction component of $`r MIL_PARAM`$,
so its orientation will always pass through the origin.

As plotting more than two dimensions is difficult on a bidimensional display
(and hardly possible at all for more than three dimensions with the
currently available technology),
we will limit ourselves to the bidimensional case here.
Plotting on a two-dimensional display usually requires providing
coordinates in a rectangular Cartesian system.
Therefore, we will need to compute the equivalent rectangular coordinates
of our general, possibly non-rectangular coordinates.
This implies pre-multiplying its coordinates in basis $`r LS_BASIS`$
by $`r TRANSFORM_MATRIX_TRANSP_INV`$, to find
the equivalent, orthonormalized coordinates.

Therefore, we need to define
a convenient value for $`r TRANSFORM_MATRIX_TRANSP_INV`$
that allows us to represent the test space structure and the items
in a rectangular Cartesian system.
However, to facilitate the interpretation,
we want to avoid changing the scale of the parameters.
We will thus prefer the correlation-based over the covariance-based parameters.
Thus, we define $`r TRANSFORM_MATRIX_TRANSP_INV`$
to be a square root matrix of $`r CORR_MATRIX`$.

@@

@@

1. Define $`r TRANSFORM_MATRIX_TRANSP_INV`$ such that
   $`r TRANSF_MATRIX_INV_SQ_CORR_EQ`$.
